Quantile Regressions via Method of Moments with multiple fixed effects \tnoteref{t1}

### 2023-11-13 article/article.tex
Revert "update CG"
This reverts commit 77ae13d0bd502eb1f2836fcd140a6af5ce0c6cce.

\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\journal{Journal Name}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Quantile Regressions via Method of Moments with multiple fixed effects},
  pdfauthor={Fernando Rios-Avila; Leonardo Siles; Gustavo Canavire-Bacarreza},
  pdfkeywords={Fixed effects, Linear heteroskedasticity, Location-scale
model, Quantile regression},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Quantile Regressions via Method of Moments with multiple fixed
effects}
\author[1]{Fernando Rios-Avila%
\corref{cor1}%
}
 \ead{friosavi@levy.org} 
\author[2]{Leonardo Siles%
%
}
 \ead{leonardosiles@hotmail.com} 
\author[3]{Gustavo Canavire-Bacarreza%
%
\fnref{fn1}}
 \ead{gcanavire@worldbank.org}

@@

\fntext[fn1]{The opinions expressed in this paper are those of the
authors and do not necessarily reflect the views of the World Bank, its
Board of Directors, or the countries it represents}

@@

\[q(y|\tau,x) = x'(\beta + q(\tau) \times \gamma)\]

@@

\[\bar G(\theta) = \begin{bmatrix}
\bar G_{11} & G_{12} & G_{13} \\
\bar G_{21} & \bar G_{22} & G_{23} \\
\bar G_{31} & \bar G_{32} & \bar G_{13} \\
\end{bmatrix}
\]

@@

\[\begin{aligned}
E(K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i )|X) &= f_{y|X}(q^\varepsilon_\tau x_i'\gamma +x_i'\beta) \\
&=\frac{1}{x_i'\gamma} f_{\varepsilon}(q^\varepsilon_\tau) \\
\end{aligned}
\]

>>>>

\tnotetext[t1]{The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\journal{Journal Name}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Quantile Regressions via Method of Moments with multiple fixed effects },
  pdfauthor={Fernando Rios-Avila; Leonardo Siles; Gustavo Canavire-Bacarreza},
  pdfkeywords={Fixed effects, Linear heteroskedasticity, Location-scale
model, Quantile regression},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Quantile Regressions via Method of Moments with multiple fixed
effects \tnoteref{t1}}
\author[1]{Fernando Rios-Avila%
\corref{cor1}%
}
 \ead{friosavi@levy.org} 
\author[2]{Leonardo Siles%
%
}
 \ead{leonardosiles@hotmail.com} 
\author[3]{Gustavo Canavire-Bacarreza%
%
}
 \ead{gcanavire@worldbank.org}

@@

@@

\[Q_y(\tau|x) = x'(\beta + q(\tau) \times \gamma)\]

@@

\[\bar G(\theta) = \begin{bmatrix}
\bar G_{11} & \bar G_{12} & \bar G_{13} \\
\bar G_{21} & \bar G_{22} & \bar G_{23} \\
\bar G_{31} & \bar G_{32} & \bar G_{13} \\
\end{bmatrix}
\]

@@

\[\begin{aligned}
E(K_h(q(\tau) x_i'\gamma +x_i'\beta - y_i )|X) &= f_{y|X}(q(\tau) x_i'\gamma +x_i'\beta) \\
&=\frac{1}{x_i'\gamma} f_{\varepsilon}(q(\tau)) \\
\end{aligned}
\]
